---
title: "HTMLwidgets within R Markdown"
output: 
  html_document:
    fig_height: 8
    fig_width: 10
---

[htmlwidgets](http://www.htmlwidgets.org) is a package to facilitate
the use of JavaScript-based graphics with R. A super nice feature is
that the graphics will be rendered in the appropriate way, according
to where they are called (in browser, within RStudio's plot frame,
within an R Markdown document, or as part of a Shiny app.

Here's a scatterplot that you can zoom and pan, via
[scatterD3](https://github.com/juba/scatterD3).

```{r zoomscatterplot}
n <- 100
x <- rnorm(n)
y <- rnorm(n)+x
grp <- as.numeric(y < 0)
library(scatterD3)
scatterD3(x, y, lab=paste0("pt", 1:n), col_var=grp,
          colors=c("slateblue", "Orchid"))
```

Here's a map of the area via [leaflet](http://rstudio.github.io/leaflet/)

```{r leaflet_map, message=FALSE}
library(ggmap)
addr <- c(UseR="366 Galvez St, Stanford, CA",
          Hotel="235 Hamilton Ave, Palo Alto, CA")
lonlat <- geocode(addr, source="google")
library(leaflet)
leaflet() %>%
    setView(lng= lonlat$lon[1], lat=lonlat$lat[1],
            zoom=14) %>%
    addProviderTiles("CartoDB.Positron") %>% 
    addCircleMarkers(lng=lonlat$lon, 
                     lat=lonlat$lat,
                     popup=paste0(lonlat$.id),
                     color=c("slateblue", "Orchid"),
                     fillColor=c("slateblue", "Orchid"))
```

You can make heatmaps with [d3heatmap](https://github.com/rstudio/d3heatmap). For example, here's a heatmap of a correlation matrix:

```{r d3heatmap, fig.width=6, fig.height=5}
library(d3heatmap)
d3heatmap(cor(iris[,1:4]), Rowv=FALSE, Colv=FALSE, colors="Blues")
```

For network diagrams, consider [networkD3](https://github.com/christophergandrud/networkD3).

```{r networkD3, message=FALSE}
library(networkD3)
data(MisLinks)
data(MisNodes)
# Create graph
forceNetwork(Links = MisLinks, Nodes = MisNodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             Group = "group", opacity = 0.8, zoom = TRUE)
```

Scatterplot matrices with [pairsD3](https://github.com/garthtarr/pairsD3/).

```{r pairsD3}
library(pairsD3)
pairsD3(iris[,1:4],group=iris[,5],
        labels=gsub("\\.", " ", names(iris)))
```