---
title: "About YAML"
output: html_document
---

The YAML header in Rmarkdown documents is generally easy to read and
create, but the syntax can be a bit confusing, so it's worth talking
about a bit.

[YAML](http://www.yaml.org) is sort of like
[JSON](http://www.json.org): a system for specifying complex data
structures in text.

Consider this:

```
output:
  html_document:
      toc: true
      number_sections: true
      fig_height: 6
```

This is specifying a nested, named list, like this:

```{r simple_example, eval=FALSE}
list(output=list(html_document=list(toc=TRUE, number_sections=TRUE, fig_height=6)))
```

You can use the [yaml](https://cran.r-project.org/web/packages/yaml/)
package to convert to and from YAML.

```{r from_YAML}
library(yaml)
x <- "output:\n  html_document:\n      toc: true\n      number_sections: true\n      fig_height: 6"
yaml.load(x)
```

```{r to_YAML}
y <- list(output=list(html_document=list(toc=TRUE, number_sections=TRUE, fig_height=6)))
as.yaml(y)
cat(as.yaml(y))
```

Here's a more complicated example.

```
title: "Haplotype probabilities in advanced intercross populations"
author:
- name: "Karl W. Broman"
  affiliation: "Department of Biostatistics and Medical Informatics, University of Wisconsin-Madison"
output:
  pdf_document:
    citation_package: natbib
    keep_tex: no
    template: template.tex
bibliography: ailprob.bib
biblio-style: genetics
fontfamily: mathpazo
```

The corresponding R object looks like this:

```{r complex_yaml}
x <- 'title: "Haplotype probabilities in advanced intercross populations"
author:
- name: "Karl W. Broman"
  affiliation: "Department of Biostatistics and Medical Informatics, University of Wisconsin-Madison"
output:
  pdf_document:
    citation_package: natbib
    keep_tex: no
    template: template.tex
bibliography: ailprob.bib
biblio-style: genetics
fontfamily: mathpazo'
yaml.load(x)
```
