---
title: "Introduction"
runtime: shiny
---

* The format I (Ian) use the most is `html_document()`.

* Uses bootstrap, which opens up a lot of possibilities.
  
* However, there are cases where you may want or need to be a bit more-specialized.

* Looking at the source code for these can give you inspiration on how to make your own formats. 

## Output formats

This is the set of instructions that tells `render()` what to do with the Rmd file sent to it. We'll get a feel for how it works by looking at a few examples. 

Go through `five_minute_test.Rmd`.
  
### HTML vignette

The biggest use case for this is when you are writing a package. The CRAN folks like things to be lightweight.

If you use this, chances are you will use the devtools function `use_vignette()`.

```{r eval=FALSE}
use_vignette("fiddly_bits")
```

### Tufte

```{r}
# install.packages("tufte")
```

Provides functions that give html (`tufte_html()`) and pdf (`tufte_handout()`)

Look at (http://rstudio.github.io/tufte/)

### bookdown

Bring up (https://twitter.com/hadleywickham/status/715974377741811713).

Have a look at the [bookdown site](https://bookdown.org/).


