---
title: "Output formats"
runtime: shiny
---

Remember slide 11?

```{r eval=FALSE}
library(rmarkdown)
render('input.Rmd')
render('input.Rmd', pdf_document())
render('input.Rmd', word_document())
render('input.Rmd', beamer_presentation())
render('input.Rmd', ioslides_presentation())
```

To render a document, we need a source (`'input.Rmd'`) and a set of instructions on what to do with it (for example, `pdf_document()`.)

Look again at `five_minute_test.Rmd`. The thing we provide after `output:` is simply the name of the function to use when running `render()`.

Here are some things you can try. Using the environment window in the RStudio IDE, look at how the structure changes.

```{r eval=FALSE}
library("rmarkdown")
fmt_html_document <- html_document() 
fmt_html_document <- html_document(fig_width = 3)

fmt_pdf_document <- pdf_document()
```

Each of these is an `rmarkdown_output_format` generated using `rmarkdown::output_format()`.

Now, let's look at some of the source code. Try this:

```{r eval=FALSE}
html_document

pdf_document
```

Looking near the bottom of the source code, what differences to you see? what seems the same?

A common thing is these functions all call `rmarkdown::output_format()`, all return an `rmarkdown_output_format` object.

### Others

Examine source for: (maybe have the github pages handy)

* `rmarkdown::html_vignette` 
* `rmarkdown::rtf_document`
* `tufte::tufte_html`
* `tufte::tufte_handout`

### What's already available

Check out http://rmarkdown.rstudio.com

### Conclusion

If you provide a function that returns an `rmarkdown_output_format` object, you have a custom format.


