---
title: "rmarkdown output format"
output:
  pdf_document: default
  html_document: default
---

Here are some examples from the slides on using `render()`:

```{r eval=FALSE}
library(rmarkdown)
render('input.Rmd')
render('input.Rmd', pdf_document())
render('input.Rmd', word_document())
render('input.Rmd', beamer_presentation())
render('input.Rmd', ioslides_presentation())
```

The two arguments are the thing to render, and a set of instructions on how to render it.

## `rmarkdown_output_format` objects

The each of the functions returns an object `rmarkdown_output_format`:

```{r}
library("rmarkdown")
fmt_html_document <- html_document() 
fmt_html_document2 <- html_document(fig_width = 3)

fmt_pdf_document <- pdf_document()
```

We can compare and contrast these objects:

```{r}
str(fmt_html_document)
```

```{r}
str(fmt_html_document2)
```

```{r}
str(fmt_pdf_document)
```

## Functions that return `rmarkdown_output_format` objects

Here are some links to the source code for some instructive cases:

* [rmarkdown::html_vignette](https://github.com/rstudio/rmarkdown/blob/master/R/html_vignette.R) This is a straightfoward extension to `html_document()`
* [rmarkdown::rtf_document](https://github.com/rstudio/rmarkdown/blob/master/R/rtf_document.R) Check out the pandoc options.
* [tufte::tufte_html](https://github.com/rstudio/tufte/blob/master/R/html.R), [tufte::tufte_handout](https://github.com/rstudio/tufte/blob/master/R/handout.R) These do not use the API, but modify the object after it has been generated.



